Attack Graph Generation for Micro-service Architecture

### 2018-09-19 paper_own_docker/chapters/method.tex
one small run on the first sections of the method

\section{METHOD}
\label{chap:method}

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{./images/Topology_graph}
		\caption{}
		\label{TopologyGraph}
	\end{subfigure}

	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{./images/Attack_graph}
		\caption{}
		\label{AttackGraph}
	\end{subfigure}

	\caption[Two numerical solutions]{(a) Example topology graph where each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers. (b) Example resulting attack graph, where nodes correspond to a pair of container plus privilege, while edges are atomic attacks. The topology and attack graphs are a subset of the real topology and attack graphs from the Netflix OSS example.}
\end{figure}

Up to this point, we formally defined what an attack graph is. Here, we first look at how the existing components of attack graph generation for computer networks map into a microservice environment and provide a small example in Subsection \ref{chap:mapping}. We then in Subsection \ref{chap:technical} refer to the third party tools that we use to achieve this translation and present an overview of our proposed system with its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Parser Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.

\subsection{Mapping attack graphs from network to microservice perspective}
\label{chap:mapping}

In our work, we try to translate already existing attack graph generation work from computer networks into the microservices ecosystem. In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture. In this subsection, we start first by shortly introducing a famous microservice framework (Docker) and some of its terminology. We then modify the attack graph concepts mentioned above for our use-case (nodes, edges, privilege levels, pre- and postconditions). In the end, we see how this translation works in practice by demonstrating a small example.

Docker is one of the most popular and used microservice frameworks currently available. In Docker, a distinction is being made between the terms image, container and service. An image is an executable package that includes everything needed to run an application, a container is a runtime instance of an image and service represents a container in production. A service only runs one image, but it codifies the way that image runs, what ports it should use, how many replicas of the container should run so the service has the capacity it needs \cite{merkel2014docker}. In our work, we treat these terms equally, since we are doing a static and not runtime attack graph analysis.

Privileges play a central role in this attack graph generation. We model the privileges in a hierarchy. The privileges in ascending order are None, VOS(User), VOS(Admin), OS(User) and OS(Admin). VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine. However in our case, unlike hosts connected in a computer network, these privileges are adapted to images and not virtual machines. On the other side, The keyword OS means that the host machine has been compromised. Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}. None means that no privilege is obtained, User that only a subset of user level privileges are available, while Admin grants control over the whole system.

As mentioned above, nodes and edges are the basic building blocks of an attack graph. Nodes in this attack graph model are represented as a combination of docker images and their respective privilege levels, while edges are connections between node pairs accompanied by the vulnerabilities that are being exploited as descriptors. The starting node of an edge denotes the container from which the attack is performed and the privilege level that an attacker needs to have to exploit a given vulnerability. The end node of an edge is the container which is compromised and its privilege level obtained as a result of a successful vulnerability exploitation. In order for an attacker to exploit a given vulnerability, certain preconditions have to be met. Once an attacker exploits this vulnerability, he gains the privilege of the target container as a postcondition and an edge is added to the attack graph. Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}. The pre- and postcondition rules use the fields defined by NVD, as well as an occurrence of specific keywords from the CVEs descriptions \cite{booth2013national}.

@@

>>>>

\section{METHOD}
\label{chap:method}
We already defined an attack graph. We, now, look at how the existing components of attack graph generation for computer networks map into a microservice environment, we illustrate the concepts using a small example in Subsection \ref{chap:mapping}. We then, in Subsection \ref{chap:technical}, present the tools that we use to achieve this mapping and present an overview of our proposed system and its components: Topology Parser in Subsection \ref{chap:topology_p}, Vulnerability Parser in Subsection \ref{chap:vulnerability_p} and Attack Graph Parser Subsection \ref{chap:attack_graph_p} with the Breath-first Search graph traversal algorithm in Subsection \ref{chap:bfs}.

\subsection{From Network Nodes to Microservices}
\label{chap:mapping}
% abit reptative 
In our work, we adapt already existing attack graph generation methods from computer networks to the microservices ecosystem. In order to do this, we identify the different components and find a compatible replacement that can be used in a microservice architecture. In this subsection, we start first by shortly introducing a famous microservice framework (Docker) and some of its terminology. We then modify the attack graph concepts mentioned in Subsection \ref{chap:attack_graphs}: nodes, edges, privilege levels, pre- and postconditions to match our use-case. We illustrate the whole idea  by demonstrating a small example.

Docker is one of the most popular and used containerization frameworks currently available. In Docker, a distinction is being made between the terms \textit{image}, \textit{container} and \textit{service}. An \textit{image} is an executable package that includes everything needed to run an application, a \textit{container} is a runtime instance of an image, and a \textit{service} represents a container in production. A service only runs one image, but it codifies the way that image runs, what ports it should use, how many replicas of the container should run so the service has the capacity it needs \cite{merkel2014docker}. In our work, we construct attack graphs by statically analyzing the topology of the containers, hence, we treat these terms equally.

Privileges play a central role in the generation if attack graphs. Traditionally, the privileges are modeled as a hierarchy that varies in the access type (\textit{User, Admin}), and the access scope (Virtual machine VOS, host machine OS). The exhaustive list of privileges, that are used in this paper, are: \textit{None, VOS(User), VOS(Admin), OS(User) and OS(Admin)}. VOS means that the privilege is exclusive to a virtual machine, while not affecting the host machine. However in our case, unlike hosts connected in a computer network, these privileges are adapted to images and not virtual machines. On the other side, the keyword OS means that the  host machine can be controlled by a user who has this privilege. Since VOS are isolated from host machines and their exploitation does not imply the exploitation of the host machine, they are in the lower level of hierarchy \cite{aksu2018automated}. None means that no privilege is obtained, User means only a subset of user level privileges are available, while Admin grants control over the whole system.

\textbf{TODO this paragraph is very hard to follow. it is very important, i tried a bit with it but please try to re-phrase.. what is starting node and the end node of the edge and how to decide to add an edge. Maybe try to rephrase by saying between a two connected images we add a node if .......}\\
As mentioned earlier, \textit{nodes} and \textit{edges} are the basic building blocks of an attack graph. \textit{Nodes} are represented as a combination of docker images and their respective compromise level (presented as the privilege granted to the attacker), while edges are connections between images represented by the vulnerabilities that are being exploited as descriptors. The starting node of an edge denotes the image from which the attack is performed and the required privilege level to exploit a given vulnerability. The end node of an edge is the image which is compromised and its privilege level obtained as a result of a successful vulnerability exploitation. In order for an attacker to exploit a given vulnerability, certain preconditions have to be met. Once attackers exploits this vulnerability, they gain the privilege of the target container as a postcondition and an edge is added to the attack graph. Both the pre- and postconditions in this work are transformed from pre- and postcondition rules manually selected and evaluated by experts in existing work \cite{aksu2018automated}. The pre- and postcondition rules use the fields defined by NVD, as well as an occurrence of specific keywords from the CVEs descriptions \cite{booth2013national}.

@@

\textbf{TODO shorten all the captions, they should be one line, and add all the description to the text. this goes to all the figures and table..}\\
\begin{figure*}[!h]
	\centering
	\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=.5\linewidth]{./images/Topology_graph}
		\caption{}
		\label{TopologyGraph}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=.5\linewidth]{./images/Attack_graph}
		\caption{}
		\label{AttackGraph}
	\end{subfigure}

	\caption[Two numerical solutions]{(a) Example topology graph where each node denote container(plus Docker Deamon and Outside) and each edge denotes a connection between two containers. (b) Example resulting attack graph, where nodes correspond to a pair of container plus privilege, while edges are atomic attacks. The topology and attack graphs are a subset of the real topology and attack graphs from the Netflix OSS example.}
\end{figure*}
